Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2015-03-04 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
changing axis label from "MinChW" to "Minimum Channel Width"
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4580 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
TVLSI requires at least 5 Index terms. We had 4. I added one more: CAD.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4586 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Commented on interposer crossings as contributing to path delay
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4591 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Algorithms, FPGA, Silicon interposer, 2.5D ICs. 
\end{IEEEkeywords}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{placer_opt_minChW.eps}
\caption{Impact of placer optimizations on minimum channel width.}
\label{fig:comparison_minW}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{additional_fanins.eps}
\caption{Adding up to 8 extra fanins to interposer wire muxes helps reduce minimum channel width.}
\label{fig:additional_fanins}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{minChW.eps}
\caption{Minimum channel width vs. \textit{\% wires cut} for 2 dice and $1ns$ of \textit{delay increase}.}
\label{fig:standard_minW}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{numberofcrossingwires_new.eps}
\caption{Geometric mean of required intra-die minimum channel width vs. geometric mean of the number of wires crossing the interposer for 2 dice and $1ns$ of \textit{delay increase}.}
\label{fig:crossingwires}
\end{figure}

@@

Systems with more dice are slower; on average the critical path delay is 40\% higher for a four-die system than a two-die system. This speed difference is not significantly affected by the \textit{\% wires cut}.
\begin{figure}[!htbp]
\centering
\input{crit_path_4part}
\caption{Impact of number of dice on critical path delay.}
\label{fig:crit_path_4part}
\end{figure}

>>>>

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Algorithms, FPGA, Silicon interposer, 2.5D ICs, CAD. 
\end{IEEEkeywords}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{placer_opt_minChW_2.eps}
\caption{Impact of placer optimizations on minimum channel width.}
\label{fig:comparison_minW}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{additional_fanins_2.eps}
\caption{Adding up to 8 extra fanins to interposer wire muxes helps reduce minimum channel width.}
\label{fig:additional_fanins}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{minChW_2.eps}
\caption{Minimum channel width vs. \textit{\% wires cut} for 2 dice and $1ns$ of \textit{delay increase}.}
\label{fig:standard_minW}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{numberofcrossingwires_new_2.eps}
\caption{Geometric mean of required intra-die minimum channel width vs. geometric mean of the number of wires crossing the interposer for 2 dice and $1ns$ of \textit{delay increase}.}
\label{fig:crossingwires}
\end{figure}

@@

As shown in \ref{fig:crit_path_4part}, systems with more dice are slower; on average the critical path delay is 40\% higher for a four-die system than a two-die system. This speed difference is not significantly affected by the \textit{\% wires cut}. This suggests that the main cause of the slowdown is due to interposer crossings, rather than wire congestion.
\begin{figure}[!htbp]
\centering
\input{crit_path_4part}
\caption{Impact of number of dice on critical path delay.}
\label{fig:crit_path_4part}
\end{figure}
